resistanceModelNotesAndy

### 2015-07-22 resistanceModelNotesAndy.Rmd
notes

check that the example runs still support the args the way they did before

@@

@@

1. set 1000 runs to do tonight

@@

>>>>

** 21/7/15 **
check that the example runs still support the args the way they did before

@@

I'm a bit worried that the post-processed results for the new100 runs seem not to have changed even though

** 22/7/15 **
analysing 1000 rereruns

betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
               0.223                0.245                0.243 
betterMix2Seq_cP0.1 betterMix2Seq_cP0.25  betterMix2Seq_cP0.5 
               0.558                0.563                0.534 
betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
               0.820                0.747                0.677

rounded
betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
               0.22                0.25                0.24
betterMix2Seq_cP0.1 betterMix2Seq_cP0.25  betterMix2Seq_cP0.5 
               0.56                0.56                0.53
betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
               0.82                0.75                0.68

20% better :
 betterMix1Seq20_cP0.1 betterMix1Seq20_cP0.25  betterMix1Seq20_cP0.5 
                 0.163                  0.178                  0.182 
 betterMix2Seq20_cP0.1 betterMix2Seq20_cP0.25  betterMix2Seq20_cP0.5 
                 0.283                  0.302                  0.283 
 betterMix3Seq20_cP0.1 betterMix3Seq20_cP0.25  betterMix3Seq20_cP0.5 
                 0.622                  0.536                  0.458 
rounded               
 betterMix1Seq20_cP0.1 betterMix1Seq20_cP0.25  betterMix1Seq20_cP0.5 
                 0.16                  0.18                  0.18 
 betterMix2Seq20_cP0.1 betterMix2Seq20_cP0.25  betterMix2Seq20_cP0.5 
                 0.28                  0.30                  0.28 
 betterMix3Seq20_cP0.1 betterMix3Seq20_cP0.25  betterMix3Seq20_cP0.5 
                 0.62                  0.54                  0.46

reran trees

Best ones :

to try to find an approximate general rule

Favouring mixtures over sequential use.
insecticide effectiveness (phi) > 0.7
exposure < 0.7

e.g. see treebetterMix2Seq_cP0.5.jpg

I haven't done 20% better trees yet. Should I ?

@@

1. choose 1 tree to present to Ian & maybe this should be the most useful applied one ?
(which might be mix2 at 20% & 50% resistance)

@@

1. I could add the combined mixture/individual (strategy 2) as a dotted line to plotcurtis_f2_generic()
(and then could even add labels of 1,2,3 to where they cross the 50% line)
